Response to reviewers

### 2025-01-23 Analysis/04_Summarise_results.Rmd
updated fecking tables

## Making the fancy tables for the models
model_table_2d  <- fancy.table(model_fits_2d, columns = list(c(3,4), 5))
model_table_3d  <- fancy.table(model_fits_3d, columns = list(c(3,4), 5))
model_table_4d  <- fancy.table(model_fits_4d, columns = list(c(3,4), 5))
model_table_5d  <- fancy.table(model_fits_5d, columns = list(c(3,4), 5))
model_table_8d  <- fancy.table(model_fits_8d, columns = list(c(3,4), 5))
model_table_emp <- fancy.table(model_fits_emp, columns = list(c(3,4), 5))
## For the differences
columns_diff_ses <- list(c(1,3), 4)
columns_diff_ses <- c(columns_diff_ses,
                      lapply(columns_diff_ses, `+`, 4),
                      lapply(columns_diff_ses, `+`, 8),
                      lapply(columns_diff_ses, `+`, 12))
null_table_2d   <- fancy.table(null_differences_2d, columns = columns_diff_ses, digits = 2)
null_table_3d   <- fancy.table(null_differences_3d, columns = columns_diff_ses, digits = 2)
null_table_4d   <- fancy.table(null_differences_4d, columns = columns_diff_ses, digits = 2)
null_table_5d   <- fancy.table(null_differences_5d, columns = columns_diff_ses, digits = 2)
null_table_8d   <- fancy.table(null_differences_8d, columns = columns_diff_ses, digits = 2)
null_table_emp  <- fancy.table(null_differences_emp, columns = list(c(1,3), 4, c(1,3)+4, 4+4), digits = 2)

@@

```{r, echo = FALSE, eval = FALSE}
# rownames(model_table_2d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
change.names <- function(table, fancy_names, output = "xtable", colnames = FALSE) {
  if(output == "xtable") {
    ## Format the row names for xtable
    ## split should be \\ and the third element should be \texttt{}
    row_names <- sapply(fancy_names, strsplit, split = "\\n")
    add.ttt <- function(x) {
      x[[3]] <- paste0("\\texttt{", x[[3]], "}")
      return(x)
    }
    row_names <- lapply(row_names, add.ttt)
    row_names <- lapply(row_names, function(x) paste(x, collapse = "\\\\"))
  }
  if(colnames) {
    colnames(table) <- gsub("equalizing", "EQ", colnames(table))
    colnames(table) <- gsub("facilitation", "FA", colnames(table))
    colnames(table) <- gsub("filtering", "FI", colnames(table))
    colnames(table) <- gsub("competition", "CO", colnames(table))
    colnames(table) <- gsub("rm", "", colnames(table))
  }
  rownames(table) <- row_names
  return(table)
}
# kable(model_table_2d, caption = "Results of the model scaled metric ~ removal level per stressor (2D)", align = "c")
print(xtable(change.names(model_table_2d, fancy_names), caption = "Results of the model scaled metric ~ removal level per stressor (2D)"), file = "../Manuscript/Tables/results_model2d.tex")

print(xtable(change.names(model_table_4d, fancy_names), caption = "Results of the model scaled metric ~ removal level per stressor (4D)"), file = "../Manuscript/Tables/results_model4d.tex")

print(xtable(change.names(model_table_8d, fancy_names), caption = "Results of the model scaled metric ~ removal level per stressor (8D)"), file = "../Manuscript/Tables/results_model8d.tex")

print(xtable(change.names(model_table_emp, fancy_names), caption = "Results of the model scaled metric ~ removal level per stressor (empirical data)"), file = "../Manuscript/Tables/results_empirical.tex")
```

@@

```{r, echo = FALSE, eval = FALSE}
print(xtable(change.names(null_table_2d[, 1:8], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences2d_1.tex")

print(xtable(change.names(null_table_2d[, 9:16], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). FA = facilitation; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences2d_2.tex")

print(xtable(change.names(null_table_2d[, 17:24], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). FI = filtering; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences2d_3.tex")

print(xtable(change.names(null_table_2d[, 25:32], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D).CO = competition; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences2d_4.tex")

print(xtable(change.names(null_table_4d[, 1:8], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences4d_1.tex")

print(xtable(change.names(null_table_4d[, 9:16], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D). FA = facilitation; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences4d_2.tex")

print(xtable(change.names(null_table_4d[, 17:24], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D). FI = filtering; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences4d_3.tex")

print(xtable(change.names(null_table_4d[, 25:32], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D).CO = competition; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences4d_4.tex")

print(xtable(change.names(null_table_8d[, 1:8], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences8d_1.tex")

print(xtable(change.names(null_table_8d[, 9:16], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D). FA = facilitation; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences8d_2.tex")

print(xtable(change.names(null_table_8d[, 17:24], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D). FI = filtering; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences8d_3.tex")

print(xtable(change.names(null_table_8d[, 25:32], fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D).CO = competition; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differences8d_4.tex")

print(xtable(change.names(null_table_emp, fancy_names, colnames = TRUE),
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each
stressor (empirical); d = difference, s = standardised effect size. Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1."),
  file = "../Manuscript/Tables/results_differencesempirical.tex")
```

>>>>

## Making the fancy tables for the models
model_table_2d  <- fancy.table(model_fits_2d, columns = list(c(3,4), 5))
model_table_3d  <- fancy.table(model_fits_3d, columns = list(c(3,4), 5))
model_table_4d  <- fancy.table(model_fits_4d, columns = list(c(3,4), 5))
model_table_5d  <- fancy.table(model_fits_5d, columns = list(c(3,4), 5))
model_table_8d  <- fancy.table(model_fits_8d, columns = list(c(3,4), 5))
model_table_emp <- fancy.table(model_fits_emp, columns = list(c(3,4), 5))
## For the differences
columns_diff_ses <- list(c(1,3), 4)
columns_diff_ses <- c(columns_diff_ses,
                      lapply(columns_diff_ses, `+`, 4),
                      lapply(columns_diff_ses, `+`, 8),
                      lapply(columns_diff_ses, `+`, 12))

null_table_2d   <- fancy.table(null_differences_2d, columns = columns_diff_ses, digits = 2)
null_table_3d   <- fancy.table(null_differences_3d, columns = columns_diff_ses, digits = 2)
null_table_4d   <- fancy.table(null_differences_4d, columns = columns_diff_ses, digits = 2)
null_table_5d   <- fancy.table(null_differences_5d, columns = columns_diff_ses, digits = 2)
null_table_8d   <- fancy.table(null_differences_8d, columns = columns_diff_ses, digits = 2)
null_table_emp  <- fancy.table(null_differences_emp, columns = list(c(1,3), 4, c(1,3)+4, 4+4), digits = 2)

@@

```{r, echo = FALSE, eval = FALSE}
# rownames(model_table_2d) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
change.names <- function(table, fancy_names, output = "xtable", colnames = FALSE) {
  if(output == "xtable") {
    ## Format the row names for xtable
    ## split should be \\ and the third element should be \texttt{}
    row_names <- sapply(fancy_names, strsplit, split = "\\n")
    add.ttt <- function(x) {
      x[[3]] <- paste0("\\texttt{", x[[3]], "}")
      return(x)
    }
    row_names <- lapply(row_names, add.ttt)
    row_names <- lapply(row_names, function(x) paste(x, collapse = "\\\\"))
  }
  if(colnames) {
    colnames(table) <- gsub("equalizing", "EQ", colnames(table))
    colnames(table) <- gsub("facilitation", "FA", colnames(table))
    colnames(table) <- gsub("filtering", "FI", colnames(table))
    colnames(table) <- gsub("competition", "CO", colnames(table))
    colnames(table) <- gsub("rm", "", colnames(table))
  }
  rownames(table) <- row_names
  return(table)
}
# kable(model_table_2d, caption = "Results of the model scaled metric ~ removal level per stressor (2D)", align = "c")
print(xtable(change.names(model_table_2d, rev(fancy_names)), caption = "Results of the model scaled metric $\\sim$ removal level per stressor (2D)"), file = "../Manuscript/Tables/results_model2d.tex")

print(xtable(change.names(model_table_4d, rev(fancy_names)), caption = "Results of the model scaled metric $\\sim$ removal level per stressor (4D)"), file = "../Manuscript/Tables/results_model4d.tex")

print(xtable(change.names(model_table_8d, rev(fancy_names)), caption = "Results of the model scaled metric $\\sim$ removal level per stressor (8D)"), file = "../Manuscript/Tables/results_model8d.tex")

print(xtable(change.names(model_table_emp, rev(fancy_names)), caption = "Results of the model scaled metric $\\sim$ removal level per stressor (empirical data)"), file = "../Manuscript/Tables/results_empirical.tex")
```

@@

```{r, echo = FALSE, eval = FALSE}
print(xtable(change.names(null_table_2d[, 1:8], rev(fancy_names)), colnames = TRUE,
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \\textit{g} with a correction for small-sample bias (using \\texttt{effectsize::hedges_g})."),
  file = "../Manuscript/Tables/results_differences2d_1.tex")

print(xtable(change.names(null_table_2d[, 9:16], rev(fancy_names)), colnames = TRUE,
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). FA = facilitation; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \\textit{g} with a correction for small-sample bias (using \\texttt{effectsize::hedges_g})."),
  file = "../Manuscript/Tables/results_differences2d_2.tex")

print(xtable(change.names(null_table_2d[, 17:24], rev(fancy_names)), colnames = TRUE,
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). FI = filtering; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \\textit{g} with a correction for small-sample bias (using \\texttt{effectsize::hedges_g})."),
  file = "../Manuscript/Tables/results_differences2d_3.tex")

print(xtable(change.names(null_table_2d[, 25:32], rev(fancy_names)), colnames = TRUE,
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D).CO = competition; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \\textit{g} with a correction for small-sample bias (using \\texttt{effectsize::hedges_g})."),
  file = "../Manuscript/Tables/results_differences2d_4.tex")

print(xtable(change.names(null_table_4d[, 1:8], rev(fancy_names)), colnames = TRUE,
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \\textit{g} with a correction for small-sample bias (using \\texttt{effectsize::hedges_g})."),
  file = "../Manuscript/Tables/results_differences4d_1.tex")

print(xtable(change.names(null_table_4d[, 9:16], rev(fancy_names)), colnames = TRUE,
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D). FA = facilitation; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \\textit{g} with a correction for small-sample bias (using \\texttt{effectsize::hedges_g})."),
  file = "../Manuscript/Tables/results_differences4d_2.tex")

print(xtable(change.names(null_table_4d[, 17:24], rev(fancy_names)), colnames = TRUE,
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D). FI = filtering; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \\textit{g} with a correction for small-sample bias (using \\texttt{effectsize::hedges_g})."),
  file = "../Manuscript/Tables/results_differences4d_3.tex")

print(xtable(change.names(null_table_4d[, 25:32], rev(fancy_names)), colnames = TRUE,
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (4D).CO = competition; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \\textit{g} with a correction for small-sample bias (using \\texttt{effectsize::hedges_g})."),
  file = "../Manuscript/Tables/results_differences4d_4.tex")

print(xtable(change.names(null_table_8d[, 1:8], rev(fancy_names)), colnames = TRUE,
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \\textit{g} with a correction for small-sample bias (using \\texttt{effectsize::hedges_g})."),
  file = "../Manuscript/Tables/results_differences8d_1.tex")

print(xtable(change.names(null_table_8d[, 9:16], rev(fancy_names)), colnames = TRUE,
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D). FA = facilitation; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \\textit{g} with a correction for small-sample bias (using \\texttt{effectsize::hedges_g})."),
  file = "../Manuscript/Tables/results_differences8d_2.tex")

print(xtable(change.names(null_table_8d[, 17:24], rev(fancy_names)), colnames = TRUE,
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D). FI = filtering; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \\textit{g} with a correction for small-sample bias (using \\texttt{effectsize::hedges_g})."),
  file = "../Manuscript/Tables/results_differences8d_3.tex")

print(xtable(change.names(null_table_8d[, 25:32], rev(fancy_names)), colnames = TRUE,
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (8D).CO = competition; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\\%, 40\\%, 60\\% and 80\\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \\textit{g} with a correction for small-sample bias (using \\texttt{effectsize::hedges_g})."),
  file = "../Manuscript/Tables/results_differences8d_4.tex")

print(xtable(change.names(null_table_emp[, ], rev(fancy_names)), colnames = TRUE,
  caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (empirical); d = difference, s = standardised effect size. Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \\textit{g} with a correction for small-sample bias (using \\texttt{effectsize::hedges_g})."),
  file = "../Manuscript/Tables/results_differencesempirical.tex")
```

### 2025-01-23 Manuscript/Tables/results_differences2d_1.tex
updated fecking tables

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Nov 28 15:22:09 2024
\begin{table}[ht]
\scriptsize
\centering
\begin{tabular}{rllllllll}
  \hline
 & EQ.d\_1 & EQ.ses\_1 & EQ.d\_2 & EQ.ses\_2 & EQ.d\_3 & EQ.ses\_3 & EQ.d\_4 & EQ.ses\_4 \\ 
  \hline
Functional evenness\\distances\\\texttt{FD::dbFD()\$FEve} & 66.11*** & 4.1 & 68.86*** & 3.87 & 60.36*** & 3 & 43.83*** & 2.01 \\ 
  Functional evenness\\dendrogram\\\texttt{BAT::evenness} & 43.52*** & 4.02 & 41.95*** & 3.83 & 34.67*** & 2.89 & 23.62*** & 1.85 \\ 
  Functional evenness\\hypervolume\\\texttt{BAT::kernel.evenness} & 36.44*** & 4.88 & 41.74*** & 5.17 & 39.04*** & 4.21 & 30.16*** & 2.99 \\ 
  Functional evenness\\probability density\\\texttt{TPD::REND} & 31.3*** & 5.32 & 37.36*** & 4.98 & 33.84*** & 3.53 & 23.2*** & 2.13 \\ 
  Rao's quadratic entropy\\distances\\\texttt{FD::dbFD()\$RaoQ} & 0.11*** & 3.48 & 0.05*** & 1.64 & 0.01*** & 0.44 & -0.01*** & -0.25 \\ 
  Functional dispersion\\dendrogram\\\texttt{BAT::dispersion} & 2.06*** & 4.98 & 1.78*** & 4.39 & 1.38*** & 3.23 & 0.92*** & 2.06 \\ 
  Functional dispersion\\hypervolume\\\texttt{BAT::kernel.dispersion} & 0.24*** & 2.01 & 0.17*** & 1.51 & 0.11*** & 1.03 & 0.06*** & 0.59 \\ 
  Divergence\\probability density\\\texttt{TPD::REND} & 2.81*** & 20.32 & 2.07*** & 18.96 & 1.43*** & 15.61 & 0.82*** & 11.23 \\ 
  Alpha diversity\\dendrogram\\\texttt{BAT::alpha} & 0.09*** & 4.35 & 0.04*** & 2.12 & 0.01*** & 0.7 & -0.01*** & -0.49 \\ 
  Functional richness\\convex hull\\\texttt{BAT::hull.alpha} & -0.33*** & -5.46 & -0.24*** & -4.94 & -0.16*** & -3.81 & -0.09*** & -2.12 \\ 
  Functional richness\\hypervolume\\\texttt{BAT::kernel.alpha} & 0 & -0.01 & 0* & -0.18 & 0*** & -0.27 & 0*** & -0.23 \\ 
  Functional richness\\probability density\\\texttt{TPD::REND} & -0.02*** & -0.69 & -0.03*** & -1.32 & -0.03*** & -1.58 & -0.03*** & -1.54 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1.} 
\end{table}

>>>>

% latex table generated in R 4.4.2 by xtable 1.8-4 package
% Thu Jan 23 18:55:43 2025
\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{rllllllll}
  \hline
 & EQ.d\_rm1 & EQ.ses\_rm1 & EQ.d\_rm2 & EQ.ses\_rm2 & EQ.d\_rm3 & EQ.ses\_rm3 & EQ.d\_rm4 & EQ.ses\_rm4 \\ 
  \hline
Functional richness\\ probability density\\ \texttt{TPD::REND} & 66.11*** & 4.1 & 68.86*** & 3.87 & 60.36*** & 3 & 43.83*** & 2.01 \\ 
  Functional richness\\ hypervolume\\ \texttt{BAT::kernel.alpha} & 43.52*** & 4.02 & 41.95*** & 3.83 & 34.67*** & 2.89 & 23.62*** & 1.85 \\ 
  Functional richness\\ convex hull\\ \texttt{BAT::hull.alpha} & 36.44*** & 4.88 & 41.74*** & 5.17 & 39.04*** & 4.21 & 30.16*** & 2.99 \\ 
  Alpha diversity\\ dendrogram\\ \texttt{BAT::alpha} & 31.3*** & 5.32 & 37.36*** & 4.98 & 33.84*** & 3.53 & 23.2*** & 2.13 \\ 
  Divergence\\ probability density\\ \texttt{TPD::REND} & 0.11*** & 3.48 & 0.05*** & 1.64 & 0.01*** & 0.44 & -0.01*** & -0.25 \\ 
  Functional dispersion\\ hypervolume\\ \texttt{BAT::kernel.dispersion} & 2.06*** & 4.98 & 1.78*** & 4.39 & 1.38*** & 3.23 & 0.92*** & 2.06 \\ 
  Functional dispersion\\ dendrogram\\ \texttt{BAT::dispersion} & 0.24*** & 2.01 & 0.17*** & 1.51 & 0.11*** & 1.03 & 0.06*** & 0.59 \\ 
  Rao's quadratic entropy\\ distances\\ \texttt{FD::dbFD()\$RaoQ} & 2.81*** & 20.32 & 2.07*** & 18.96 & 1.43*** & 15.61 & 0.82*** & 11.23 \\ 
  Functional evenness\\ probability density\\ \texttt{TPD::REND} & 0.09*** & 4.35 & 0.04*** & 2.12 & 0.01*** & 0.7 & -0.01*** & -0.49 \\ 
  Functional evenness\\ hypervolume\\ \texttt{BAT::kernel.evenness} & -0.33*** & -5.46 & -0.24*** & -4.94 & -0.16*** & -3.81 & -0.09*** & -2.12 \\ 
  Functional evenness\\ dendrogram\\ \texttt{BAT::evenness} & 0 & -0.01 & 0* & -0.18 & 0*** & -0.27 & 0*** & -0.23 \\ 
  Functional evenness\\ distances\\ \texttt{FD::dbFD()\$FEve} & -0.02*** & -0.69 & -0.03*** & -1.32 & -0.03*** & -1.58 & -0.03*** & -1.54 \\ 
   \hline
\end{tabular}
\caption{Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor (2D). EQ = equalising; d = difference, s = standardised effect size; 1 to 4 correspond to the levels of data removal (20\%, 40\%, 60\% and 80\%). Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1. Standardised effect size was calculated using the Hedges' \textit{g} with a correction for small-sample bias.} 
\end{table}
